Do expert pianists adapt their pedagogical demonstrations to novices' skills?

### 2022-12-01 paper/manuscript.Rmd
change chunk names
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

```{r ioi-plot, include = FALSE}
ioi_all_plot <- ggplot(ioi[Category != "baseline"], aes(x = Articulation, y = Mean, color = Dynamics)) +
  geom_boxplot(outlier.shape = NA, position = position_dodge2(preserve = "single")) +
  geom_hline(yintercept = 300, linetype = "dashed") +
  geom_point(position = position_jitterdodge(jitter.width = 0.25), alpha = 0.5) + labs(y = "IOI (ms)", title = "IOI") + scale_y_continuous(breaks = seq(240, 320, 20), limits = c(240, 320)) +
  scale_color_aaas() +
  theme_pubr(base_size = 20, base_family = "Helvetica")

@@

```{r kot-plot, include = FALSE}
leg_all_plot <- ggplot(kot[Subcomponent1 == "Legato" & Category != "baseline"], aes(x = Articulation, y = Mean, color = Dynamics)) +
  geom_boxplot(outlier.shape = NA) +
  geom_point(position = position_jitterdodge(jitter.width = 0.25), alpha = 0.5) +
  labs(y = "KOT (ms)", title = "KOT - Legato") + scale_y_continuous(breaks = seq(-20, 140, 40), limits = c(-20, 140)) +
  scale_color_aaas() +
  theme_pubr(base_size = 20, base_family = "Helvetica")

@@

```{r vel-plot, include = FALSE}
for_all_plot <- ggplot(vel[Subcomponent2 == "Forte" & Category != "baseline"], aes(x = Dynamics, y = Mean, color = Articulation)) +
  geom_boxplot(outlier.shape = NA) +
  geom_point(position = position_jitterdodge(jitter.width = 0.25), alpha = 0.5) +
  labs(y = "KV (0-127)", title = "KV - Forte") + scale_y_continuous(breaks = seq(60, 100, 10), limits = c(60, 100)) +
  scale_color_aaas() +
  theme_pubr(base_size = 20, base_family = "Helvetica")

@@

```{r vel-diff-plot, include = FALSE}
ftop_all_plot <- ggplot(vel_diff[Subcomponent2 == "FtoP" & Category != "baseline"], aes(x = Dynamics, y = Mean, color = Articulation)) +
  geom_boxplot(outlier.shape = NA) +
  geom_point(position = position_jitterdodge(jitter.width = 0.25), alpha = 0.5) +
  labs(y = "KV Difference (-127-127)", title = "KV Difference - FtoP") + scale_y_continuous(breaks = seq(-40, 10, 10), limits = c(-40, 10)) +
  scale_color_aaas() +
  theme_pubr(base_size = 20, base_family = "Helvetica")

>>>>

```{r ioi-plot-1, include = FALSE}
ioi_all_plot <- ggplot(ioi[Category != "baseline"], aes(x = Articulation, y = Mean, color = Dynamics)) +
  geom_boxplot(outlier.shape = NA, position = position_dodge2(preserve = "single")) +
  geom_hline(yintercept = 300, linetype = "dashed") +
  geom_point(position = position_jitterdodge(jitter.width = 0.25), alpha = 0.5) + labs(y = "IOI (ms)", title = "IOI") +
  scale_y_continuous(breaks = seq(240, 320, 20), limits = c(240, 320)) +
  scale_color_aaas() +
  theme_pubr(base_size = 20, base_family = "Helvetica")

@@

```{r kot-plot-1, include = FALSE}
leg_all_plot <- ggplot(kot[Subcomponent1 == "Legato" & Category != "baseline"], aes(x = Articulation, y = Mean, color = Dynamics)) +
  geom_boxplot(outlier.shape = NA) +
  geom_point(position = position_jitterdodge(jitter.width = 0.25), alpha = 0.5) +
  labs(y = "KOT (ms)", title = "KOT - Legato") + scale_y_continuous(breaks = seq(-20, 140, 40), limits = c(-20, 140)) +
  scale_color_aaas() +
  theme_pubr(base_size = 20, base_family = "Helvetica")

@@

```{r vel-plot-1, include = FALSE}
for_all_plot <- ggplot(vel[Subcomponent2 == "Forte" & Category != "baseline"], aes(x = Dynamics, y = Mean, color = Articulation)) +
  geom_boxplot(outlier.shape = NA) +
  geom_point(position = position_jitterdodge(jitter.width = 0.25), alpha = 0.5) +
  labs(y = "KV (0-127)", title = "KV - Forte") + scale_y_continuous(breaks = seq(60, 100, 10), limits = c(60, 100)) +
  scale_color_aaas() +
  theme_pubr(base_size = 20, base_family = "Helvetica")

@@

```{r vel-diff-plot-1, include = FALSE}
ftop_all_plot <- ggplot(vel_diff[Subcomponent2 == "FtoP" & Category != "baseline"], aes(x = Dynamics, y = Mean, color = Articulation)) +
  geom_boxplot(outlier.shape = NA) +
  geom_point(position = position_jitterdodge(jitter.width = 0.25), alpha = 0.5) +
  labs(y = "KV Difference (-127-127)", title = "KV Difference - FtoP") + scale_y_continuous(breaks = seq(-40, 10, 10), limits = c(-40, 10)) +
  scale_color_aaas() +
  theme_pubr(base_size = 20, base_family = "Helvetica")
